### 2021-12-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@86ebd98bc34ce6f8d63cf608c9fdb2c6906dd657 🚀

>>>>

In this last section, we generate a network using the same model as
before, with \(S = 50\) species, a connectance of \(\approx 0.16\)
(\(\xi = 0.19\)), and a training set bias of \(0.7\). The prediction
made on the complete dataset is presented in fig.~\ref{fig:ecovalid}.
Visualizing the results this way highlights the importance of
exploratory data analysis: whereas all models return a network with
interactions laying mostly on the diagonal (as expected), the Ridge
Regression is quite obviously biased. Despite this, we can see that the
ensemble is close to the initial dataset.

\includegraphics{figures/valid_ensemble.png}

The trained models were then thresholded (again by optimising
informedness), and their predictions transformed back into networks for
analysis; specifically, we measured the connectance, nestedness (REF),
modularity (REF), and entropy (REF). The results are presented in the
following table:

\begin{longtable}[]{@{}lllllllll@{}}
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) & \(Q\) &
Entropy\tabularnewline
\midrule
\endhead
Decision tree & 0.83 & 0.68 & 0.95 & 0.15 & 0.18 & 0.53 & 0.49 &
8.86\tabularnewline
BRT & 0.76 & 0.89 & 0.95 & \textbf{0.65} & 0.22 & 0.63 & 0.43 &
9.14\tabularnewline
Random Forest & \textbf{0.89} & \textbf{0.94} & \textbf{0.99} & 0.41 &
\textbf{0.17} & \textbf{0.48} & \textbf{0.49} &
\textbf{8.80}\tabularnewline
Ridge Regression & 0.67 & 0.85 & 0.89 & 0.38 & 0.27 & 1.0 & 0.26 &
9.40\tabularnewline
Ensemble & 0.84 & 0.91 & \textbf{0.99} & \textbf{0.94} & 0.19 & 0.54 &
0.48 & 8.92\tabularnewline
Data & & & & & 0.16 & 0.45 & 0.49 & 8.71\tabularnewline
\bottomrule
\end{longtable}
